### 2019-09-14 ic-journal/conclusions.tex
Merged changes in conclusions.tex

The formalisation has actually focused on the theory of
unique solution of equations and contractions. It    
 has also allowed us to further develop the theory,
notably the basic properties of rooted contraction, and the unique
solution theorem for it with respect to rooted bisimilarity. 
The formalisation brings up and exploits similarities between results
and proofs for different equivalences and preorders. Indeed we have
considered several `unique-solution' results (for various equivalences
and preorders); they share many parts of the proofs, but present a few
delicate and subtle differences in a few points. In a paper-pencil
proof, checking all details would be long and \hl{error-prone},
\hl{especially in cases in which proofs are similar to each other or
  when there are a long case analysis to be carried out.}
A theorem-prover formalisation is in this respect  helpful and reassuring.
We think that the statements in the formalisation are easy to read and
understand, as they are  close to the original statements found in
standard CCS textbooks \cite{Gorrieri:2015jt,Mil89}.

>>>>

The formalisation has actually focused on the theory of
unique solution of equations and contractions. It    
 has also allowed us to further develop the theory,
notably the basic properties of rooted contraction, and the unique
solution theorem for it with respect to rooted bisimilarity. 
The formalisation brings up and exploits similarities between results
and proofs for different equivalences and preorders. Indeed we have
considered several `unique-solution' results (for various equivalences
and preorders); they share many parts of the proofs, but present a few
delicate and subtle differences in a few points. In a paper-pencil
proof, checking all details would be long and \hl{error-prone},
\hl{especially in cases where the proofs are similar to each other or
  when there are long case analyses to be carried out.}
A theorem-prover formalisation is in this respect  helpful and reassuring.
We think that the statements in the formalisation are easy to read and
understand, as they are  close to the original statements found in
standard CCS textbooks \cite{Gorrieri:2015jt,Mil89}.
